A Proposal for an Intuitionistic Fuzzy Inference System

### 2016-01-13 paper.tex
Ejemplo
Cambio a comentario

\begin{abstract}

\end{abstract}

@@

What is a fuzzy set? \cite{zadeh1965fuzzy}

What is fuzzy logic? \cite{klir1995fuzzy}

Types of fuzzy sets. Mendel book \cite{mendel2001uncertain}

What is a fuzzy inference system?

%Empieza aquí 
%-- (Amaury) Empezaré aquí
There can be different types. Type-2 \cite{mendel2002type}, interval
t2 \cite{liang2000interval} and \cite{mendel2006interval}

Type-2 is time-consuming. Shadowed sets \cite{pedrycz1998shadowed}

What is a intuitionistic fuzzy set? \cite{atanassov1986intuitionistic}
\cite{atanassov2003intuitionistic} \cite {despi2013generalised}

@@

\section{Related Work}

@@

\section{Preliminaries}

@@

Two convenient ways of modifying a NMF and also
satisfying (\ref{intuitionistic-interval}) are the following: 1) setting
the mean and the standard deviation of the Gaussian functions to be
the same, and only vary the $height$ of the NMF,
as is depicted in Figure \ref{ifs}; and 2) setting different means and
standard deviations of the Gaussian membership and non-membership
functions, while keeping the $height$ of the MF equal
to $h_{mf} = 1 - h_{nmf}$, as this ensures that
(\ref{intuitionistic-interval}) is satisfied. An example of the latter
case is shown in Figure \ref{ifs-diff-mu-sd}. To clarify, the $height$
of the MF ($h_{mf}$) of an IFS is equal to $max(\mu(x))$, and the
$height$ of the NMF ($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.

@@

A comparison of a MF (red line) against an intuitionistic
membership function (blueline) is shown in Figure
\ref{if-membership}. The parameters for both the MF and NMF are $\mu =
50$ and $SD = 15$, but the $height$ for the NMF is set at $0.5$. This
results in an intuitionistic MF that appears to have the same mean,
but a smaller standard deviation. A more elaborated example is shown
in Figure \ref{if-membership-drastic}, where the parameters of the MF
are $\mu = 50$, $SD = 15$ and $h = 0.8$, and the parameters of the NMF
are $\mu = 30$, $SD = 20$ and $h = 0.2$. As can be noted, the
indeterminacy ($\pi$) is high in this example, which results in a
smaller $SD$ for the intuitionistic MF. Moreover, the difference in
means and standard deviations generates a change of the mean for the
intuitionistic MF.

@@

Finally, one has to defuzzify the aggregation of the $\alpha$-cut 
consequents, in order to obtain a crisp number that represents
it. There are a number of methods that can be used to defuzzify a
% Aclara que en los tipo Mamdani %% (A): ahhhhh cierto, cierto
fuzzy set, but the most frequently found in the literature is the
Center of Area (CoA), or simply centroid. One can obtain the centroid
of a classic fuzzy set A by using (\ref{center-of-area}). For an
IFS, one can use the concept of intuitionistic membership ($i\mu$) and
extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).

@@

\section{Experiments}

@@

The Mackey-Glass time series benchmark was used in order to compare
the performances of each of the FISs regarding their time series
forecasting capabilities, and a Genetic Algorithm (GA) was
used to optimize each of the FISs, so sub-optimal versions of each of
the systems were used for the comparison.

@@

\begin{enumerate}
  \item if $t_{0}$ is $A_{1}$ then $p_{t+1}$ is $C_{1}$
  \item if $t_{-6}$ is $A_{2}$ then $p_{t+1}$ is $C_{2}$
  \item if $t_{-12}$ is $A_{3}$ then $p_{t+1}$ is $C_{3}$
  \item if $t_{-18}$ is $A_{4}$ then $p_{t+1}$ is $C_{4}$
\end{enumerate}

where $t_{0}$, $t_{-6}$, $t_{-12}$, and $t_{-18}$ are points in the
Mackey-Glass time series, $t_{0}$ is the present point, $t_{-6}$ is six
points earlier than $t_{0}$, $t_{-12}$ is twelve points earlier, and
$t_{-18}$ is eighteen points earlier. $p_{t+1}$ is the predicted value
for the point $t_{1}$. $A_{1}$, $A_{2}$, $A_{3}$, and $A_{4}$ are
antecedents, and $C_{1}$, $C_{2}$, $C_{3}$, and $C_{4}$ are
consequents.

@@

Table \ref{hypothesis-tests-training} summarizes the results obtained
for each of the FISs in the training stage, as well as the t-value
obtained when calculating a Student's t-test. The same structure is
followed in Table \ref{hypothesis-tests-testing}, which shows the
results obtained for each of the FISs in the testing stage.

\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Training Stage}
  \label{hypothesis-tests-training}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value\\
    \hline
    T1-IFIS & 89.50 & 25.36 & 60 & \\
    \hline
    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 \\
    \hline
    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 \\
    \hline
    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Testing Stage}
  \label{hypothesis-tests-testing}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value\\
    \hline
    T1-IFIS & 160.99 & 65.70 & 60 & \\
    \hline
    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 \\
    \hline
    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 \\
    \hline
    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 \\
    \hline
  \end{tabular}
\end{table}

\section{Conclusion}

@@

\section{Future Work}

The current implementation of the proposed method lacks a Graphical User
Interface (GUI) where a research can conveniently design an IFIS, such as
Matlab's Type-1 Fuzzy Logic toolbox, or the Type-2 Fuzzy Logic toolbox
developed by J. R. Castro $et al.$ \cite{castro2007interval}. The
development of a GUI is planned as a next step, so researchers without
a background in the programming langague Clojure can use the
implementation for their works.

>>>>

\begin{abstract}
The concepts of intuitionistic membership, and intuitionistic center of
area are proposed in this work, in order to propose a novel method for
implementing an intuitionistic fuzzy inference system. The proposed
method was implemented and compared against type-1 fuzzy inference
systems and interval type-2 fuzzy inference systems, with uncertain
means and uncertain standard deviations, by using the
Mackey-Glass time series benchmark. A genetic algorithm was used to
optimize the parameters of each of the methods being compared, and the
results show that the intuitionistic fuzzy inference system performs
better than the other methods.
\end{abstract}

@@

Fuzzy sets were created as an extension to traditional sets, with
uncertainty in mind, by L. A. Zadeh in 1965 \cite{zadeh1965fuzzy}. This uncertainty allows an
element to be associated with a grade of membership that indicates
how much that element belongs to a set, i.e., instead of
belonging to a set (true, or 1), or not belonging (false, or 0),
such element can belong in a grade from 0 to 1, and this is known as
fuzzy logic \cite{klir1995fuzzy}.

A derivation of logical conclusions can be performed by using premises
that are assumed to be true, and this is known as inference, in
traditional logic. The same
technique can be extended to use fuzzy premises. In this case, all the
premises hold a grade of truthiness, and a fuzzy conclusion is derived
from the process. A popular method for performing such fuzzy inferences is a
Mamdani Fuzzy Inference System (FIS) \cite{mamdani1975experiment},
where the inputs are associated with fuzzy sets, and the outputs are
fuzzy sets themselves, which can be converted to crisp numbers
(this process is usually called \textit{defuzzification}). Other types of
fuzzy inference engines exist, such as Takagi-Sugeno-Kang  (TSK)
\cite{takagi1985fuzzy} and Tsukamoto \cite{tsukamoto1979approach}.

Fuzzy sets were initially criticized because they were said to
not be able to appropriately represent uncertainty. This problem was
addressed by L. A. Zadeh in 1975 \cite{zadeh1975concept} by creating the
concept of Type-2 Fuzzy Sets (T2-FS). This extension to type-1 fuzzy sets allowed the creation of
type-2 fuzzy inference systems (T2-FIS) \cite{mendel2002type}, and those systems that used the
traditional fuzzy sets are now called Type-1 Fuzzy Inference Systems
(T1-FIS). T2-FIS have been proved to work better than T1-FIS in many
situations, often problems that involve high levels of uncertainty, such as
noisy data.

Another extension to fuzzy sets, called Intuitionistic Fuzzy Sets
(IFS), was proposed by K. T. Atanassov
\cite{atanassov1986intuitionistic}. This extension adds the concepts
of indeterminacy and non-membership to traditional fuzzy sets. In
traditional fuzzy sets, the non-membership of an element is always the
complement of the membership, but in an IFS, the non-membership can be
represented by lower values (a deeper explanation of IFS is given in
Section \ref{preliminaries}). Whenever the sum of the membership and
the non-membership is less than 1, indeterminacy emerges, which
represents the grade of uncertainty of an element of being or not
being a member of a given set, with certain grade of membership. The
concept of indeterminacy allows an expression such as ``This is
somewhat tall, although I'm not very sure about my opinion.''

The use of IFSs in a traditional FIS should enable the handling of more
uncertainty, and one could prefer an Intuitionistic FIS (IFIS) to obtain
better accuracies without sacrificing time performance, as
inferences in a T2-FIS are very time consuming compared to a
T1-FIS. This is a consequence of the complex type
reducing procedure that is involved in the defuzzification stage in a
T2-FIS \cite{mendel2001uncertain}. Several improvements to the
algorithms involved in the inference process in a T2-FIS have been proposed
to alleviate this problem, such as the Karnik-Mendel algorithm
\cite{wu2009enhanced} and shadowed sets
\cite{pedrycz1998shadowed}. Nevertheless, a T2-FIS is usually several
times slower than a T1-FIS. Because of this time performance impact,
many works that require handling more uncertainty than a T1-FIS
use a particular case of T2-FIS, the Interval T2-FIS (IT2-FIS)
\cite{mendel2006interval}, which is faster than a general T2-FIS. A Type-1
Intuitionistic FIS (T1-IFIS) should perform better than a T1-FIS in terms
of accuracy (in problems involving data with high levels of
uncertainty), and should be faster than a T2-FIS. Furthermore, IFSs
can be implemented as part of a T2-FIS, giving as a result a T2-IFIS.

This work proposes a method to implement IFSs in a Mamdani FIS to
obtain a Mamdani IFIS, and presents results that prove the method as a
viable design to implement an effective IFIS. The reader can find
related works in Section \ref{related-work}. Some preliminaries are
explained in Section \ref{preliminaries} in order to better comprehend
the proposed method in Section \ref{proposed-method}. Experiments were
conducted to prove the viability of the proposed method, and they are
explained in Section \ref{experiments}. The results of the conducted
experiments are shown and explained in Section \ref{results}, and a
conclusion about the results is presented in Section
\ref{conclusion}. Finally, a description of the future work can be
found in Section \ref{future-work}.

%What is a intuitionistic fuzzy set? \cite{atanassov1986intuitionistic}
%\cite{atanassov2003intuitionistic} \cite {despi2013generalised}

@@

\section{Related Work}
\label{related-work}

@@

\section{Preliminaries}
\label{preliminaries}

@@

Two convenient ways of modifying a NMF and also
satisfying (\ref{intuitionistic-interval}) are the following: 1) setting
the mean and the standard deviation of the Gaussian functions to be
the same, and only vary the \textit{height} of the NMF,
as is depicted in Figure \ref{ifs}; and 2) setting different means and
standard deviations of the Gaussian membership and non-membership
functions, while keeping the \textit{height} of the MF equal
to $h_{mf} = 1 - h_{nmf}$, as this ensures that
(\ref{intuitionistic-interval}) is satisfied. An example of the latter
case is shown in Figure \ref{ifs-diff-mu-sd}. To clarify, the \textit{height}
of the MF ($h_{mf}$) of an IFS is equal to $max(\mu(x))$, and the
\textit{height} of the NMF ($h_{nmf}$) of an IFS is equal to $max(\nu(x))$.

@@

A comparison of a MF (red line) against an intuitionistic
membership function (blueline) is shown in Figure
\ref{if-membership}. The parameters for both the MF and NMF are $\mu =
50$ and $SD = 15$, but the \textit{height} for the NMF is set at \textit{0.5}. This
results in an intuitionistic MF that appears to have the same mean,
but a smaller standard deviation. A more elaborated example is shown
in Figure \ref{if-membership-drastic}, where the parameters of the MF
are $\mu = 50$, $SD = 15$ and $h = 0.8$, and the parameters of the NMF
are $\mu = 30$, $SD = 20$ and $h = 0.2$. As can be noted, the
indeterminacy ($\pi$) is high in this example, which results in a
smaller $SD$ for the intuitionistic MF. Moreover, the difference in
means and standard deviations generates a change of the mean for the
intuitionistic MF.

@@

Finally, one has to defuzzify the aggregation of the $\alpha$-cut 
consequents, in order to obtain a crisp number that represents
it. There are a number of methods that can be used to defuzzify a
% Aclara que en los tipo Mamdany %% (A): ahhhhh cierto, cierto
fuzzy set, but the most frequently found in the literature is the
Center of Area (CoA), or simply centroid. One can obtain the centroid
of a classic fuzzy set A by using (\ref{center-of-area}). For an
IFS, one can use the concept of intuitionistic membership ($i\mu$) and
extend (\ref{center-of-area}) to obtain (\ref{if-coa}). By
substituting $(\mu(x_{i}) + \nu(x_{i}))$ by $i\mu_{A}$, one arrives at
(\ref{if-coa-simplified}), which is a simplification of (\ref{if-coa}).

@@

\section{Experiments}
\label{experiments}

@@

The Mackey-Glass time series benchmark was used in order to compare
the performances of each of the FISs regarding their time series
forecasting capabilities, and a Genetic Algorithm (GA) was
used to optimize each of the FISs, so sub-optimal versions of each of
the systems were used for the comparison.
%M: En esta seccion creo que se

@@

\begin{enumerate}
  \item if $t_{0}$ is $A_{1}$ then $p_{t+1}$ is $C_{1}$
  \item if $t_{-6}$ is $A_{2}$ then $p_{t+1}$ is $C_{2}$
  \item if $t_{-12}$ is $A_{3}$ then $p_{t+1}$ is $C_{3}$
  \item if $t_{-18}$ is $A_{4}$ then $p_{t+1}$ is $C_{4}$
\end{enumerate}
where $t_{0}$, $t_{-6}$, $t_{-12}$, and $t_{-18}$ are points in the
Mackey-Glass time series, $t_{0}$ is the present point, $t_{-6}$ is six
points earlier than $t_{0}$, $t_{-12}$ is twelve points earlier, and
$t_{-18}$ is eighteen points earlier. $p_{t+1}$ is the predicted value
for the point $t_{1}$. $A_{1}$, $A_{2}$, $A_{3}$, and $A_{4}$ are
antecedents, and $C_{1}$, $C_{2}$, $C_{3}$, and $C_{4}$ are
consequents.

@@

Table \ref{first-hypothesis-tests-training} summarizes the results obtained
for each of the FISs in the training stage, as well as the t-value
obtained when calculating a Student's t-test. The same structure is
followed in Table \ref{first-hypothesis-tests-testing}, which shows the
results obtained for each of the FISs in the testing stage.

\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Training Stage, First Experiment}
  \label{first-hypothesis-tests-training}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI \\
    \hline
    T1-IFIS & 89.50 & 25.36 & 60 &  & \\
    \hline
    T1-FIS & 108.05 & 23.47 & 60 & -4.1584 & > 99.9\% \\
    \hline
    IT2-FIS (\(\mu\)) & 112.56 & 29.16 & 100 & -5.2597 & > 99.9\% \\
    \hline
    IT2-FIS (SD) & 102.31 & 26.08 & 300 & -3.5548 & > 99.9\% \\
    \hline
  \end{tabular}
\end{table}

% con 400
\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Training Stage, Second Experiment}
  \label{second-hypothesis-tests-training}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TR}$ & $SD_{TR}$ & $n$ & t-Value & CI\\
    \hline
    T1-IFIS & 76.22 & 16.90 & 400 & & \\
    \hline
    T1-FIS & 85.69 & 19.68 & 400 & -7.3013 & > 99.9\% \\
    \hline
    IT2-FIS (\(\mu\)) & 85.93 & 19.12 & 400 & -7.6102 & > 99.9\%\\
    \hline
    IT2-FIS (SD) & 99.78 & 19.04 & 400 & -18.508 & > 99.9\% \\
    \hline
  \end{tabular}
\end{table}

\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Testing Stage, First Experiment}
  \label{first-hypothesis-tests-testing}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value & CI \\
    \hline
    T1-IFIS & 160.99 & 65.70 & 60 &  & \\
    \hline
    T1-FIS & 194.97 & 71.97 & 60 & -2.7010 & > 99.2\%\\
    \hline
    IT2-FIS (\(\mu\)) & 192.31 & 105.75 & 100 & -2.3104 & > 97.8\% \\
    \hline
    IT2-FIS (SD) & 178.63 & 99.70 & 300 & -1.7209 & > 91.4\% \\
    \hline
  \end{tabular}
\end{table}

% con 400
\begin{table}[!t]
  \renewcommand{\arraystretch}{1.3}
  \caption{Hypothesis Tests for the Testing Stage, Second Experiment}
  \label{second-hypothesis-tests-testing}
  \centering
  \begin{tabular}{|c|c|c|c|c|c|}
    \hline
    Method & $\mu_{TS}$ & $SD_{TS}$ & $n$ & t-Value & CI\\
    \hline
    T1-IFIS & 139.38 & 95.75 & 400 &  &  \\
    \hline
    T1-FIS & 152.26 & 126.47 & 400 & -1.6239 & > 89.4\% \\
    \hline
    IT2-FIS (\(\mu\)) & 154.37 & 119.92 & 400 & -1.9536 & > 94.8\% \\
    \hline
    IT2-FIS (SD) & 175.04 & 136.91 & 400 & -4.1492 & > 99.9\%\\
    \hline
  \end{tabular}
\end{table}

\section{Conclusion}
\label{conclusion}

@@

\section{Future Work}
\label{future-work}

The current implementation of the proposed method lacks a Graphical User
Interface (GUI) where a research can conveniently design an IFIS, such as
Matlab's Type-1 Fuzzy Logic toolbox, or the Type-2 Fuzzy Logic toolbox
developed by J. R. Castro \textit{et al.} \cite{castro2007interval}. The
development of a GUI is planned as a next step, so researchers without
a background in the programming langague Clojure can use the
implementation for their works.
